### 2018-12-13 tex/paper.tex
Rearranged some sections and subections

\myparagraph{Relation between Marginal Estimation and LP Relaxation}
Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with an extension which yields the tightest bound?

@@

\myparagraph{Worst-case Optimal Submodular Extensions}
In this paper, we focus on submodular extension families $\mathcal F(.)$ which
for each instance of the energy function $E(.)$ belonging to a given class $\mathcal E$ gives a corresponding
submodular extension ${\mathcal F}(E)$. Our extensions are derived from LP relaxations. When the LP relaxation is the tightest known, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This implies that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the extension is best for every instance of the energy function. 
Also, we seek a closed-form analytical expression for $\mathcal F$. For the sake of clarity,
in the analysis that follows we use $F$ to represent ${\mathcal F}(E)$ where
the meaning is clear from context.

\mysection{Potts Model}

The Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. 
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\mysection{Hierarchical Potts Model}
\label{sec:rhst_worst-case optimal}

@@

\mysection{Higher-order Potts Model} The pairwise Potts model often fails
to capture useful image statistics because it restricts the order of the
potentials to be at most two. Higher order clique potentials can model complex
interactions of random variables, and thereby overcome this difficulty.

@@

\mysection{Fast Conditional Gradient Computation for Dense CRFs}
\label{sec:dense_crf}

>>>>

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with an extension which yields the tightest bound?

@@

\mysection{Worst-case Optimal Submodular Extensions}

\myparagraph{Worst-case Optimality}
In this paper, we focus on submodular extension families $\mathcal F(.)$ which
for each instance of the energy function $E(.)$ belonging to a given class $\mathcal E$ gives a corresponding
submodular extension ${\mathcal F}(E)$. Our extensions are derived from LP relaxations. When the LP relaxation is the tightest known, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This implies that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the extension is best for every instance of the energy function. 
Also, we seek a closed-form analytical expression for $\mathcal F$. For the sake of clarity,
in the analysis that follows we use $F$ to represent ${\mathcal F}(E)$ where
the meaning is clear from context.

\mysubsection{Potts Model}
The Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. 
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\mysubsection{Hierarchical Potts Model}
\label{sec:rhst_worst-case optimal}

@@

\mysubsection{Fast Conditional Gradient Computation for Dense CRFs}
\label{sec:dense_crf}

\mysection{Accurate Submodular Extension for Higher-order Potts Model} The pairwise Potts model often fails
to capture useful image statistics because it restricts the order of the
potentials to be at most two. Higher order clique potentials can model complex
interactions of random variables, and thereby overcome this difficulty.

@@
